\documentclass{tripos}  % Do not add anything outside the question environment
\begin{document}
\begin{question}[MockIB,year=2024,paper=2,question=11,author=rrw]{Computer Networking}

  \triposset{fullmarks=20}
  \topic{Computer Networking}

You are building software for a telco. This telco supports voice and
video communication over an ethernet network using lightly modified
commodity hardware and standard internet protocols.

Initially, you can assume that you know the sizes of all the buffers
in the network and that the underlying transport is reliable. All
hosts can keep up with the network and the network operates at 1GiB/s.

You may assume the topology of the network is fixed.

You may make reasonable assumptions about overheads.

\begin{enumerate}
\item Describe the layers of header found in an ethernet packet carrying UDP. \fullmarks{4}
\item Why might a private network running IPv4 protocols over ethernet not be suitable for making reliable telephone calls?\fullmarks{2}
\item How would you modify this network (protocols and software) so that it was suitable for making reliable telephone and video calls? \fullmarks{6}
\item Your ethernet is not totally reliable; in fact it loses about 0.1\% of the packets sent over it. Design a mechanism to cope with this. \fullmarks{4}
\item Under these assumptions, and making some reasonable assumptions about required latency, what utilisation can you support over each link? \fullmarks{4}
  \end{enumerate}


  
  
\end{question}
\end{document}
