\documentclass{tripos}  % Do not add anything outside the question environment
\begin{document}
\begin{question}[MockIB,year=2024,paper=1,question=3,author=rrw]{Economics, Law and Ethics}


\triposset{fullmarks=20}
\topic{Economics, Law and Ethics}

Airlines have a rather complex business model. They lease aircraft
(for the sake of this question, let's assume this is from the
manufacturer, M), pay for maintenance, sell tickets to customers, and bid
for landing and take-off slots at airports (which, for the sake of
this question, we will assume are all government-controlled).

Let's assume there are a limited number of routes, and two airlines -
A and B. B is attempting to grow at the expense of A; their aircraft
are newer, and have more facilities (in-flight entertainment, wifi,
etc.) but has higher fixed costs.

\begin{itemize}
\item Suggest a growth strategy for B; you may assume any reasonable market structure. \fullmarks{6}
\item Briefly outline how you would propose your strategy to the board \fullmarks{3}
\item Briefly list the government's monopoly concerns. What levers are available to them to address these? \fullmarks{5}
\item it turns out that there has been a mechanical failure on one of B's aeroplanes. This caused a piece of software, called MCheck, written by the manufacturer, but modified by B, to run. This piece of software provided access to:
  \begin{itemize}
  \item Detailed manufacturing data for M's new submarine programme.
  \item Financial and flight records from B
  \item The journey, maintenance and tech logs for all aircraft from M (ie. A's and B's).
  \item Passenger passports and loading data for the flight.
  \end{itemize}


  This data was picked up by a ransomware group and they have demanded \$1m in bitcoin to not release it.
  Who is liable, and for what?
  \fullmarks{6}
\end{itemize}
\end{question}
\end{document}


