\documentclass{tripos}  % Do not add anything outside the question environment
\begin{document}
\begin{question}[MockIA,year=2024,paper=2,question=5,author=rrw]{Introduction to Computer Architecture}

\triposset{fullmarks=20}
\topic{Introduction to Computer Architecture}

You have been given a CPU design which contains a 16-entry rotating register file and an ALU.
Each instruction for a subset of this design contains four 4-bit fields, A, B, C and D,
and a three-bit function field, F.

On each instruction:

\begin{itemize}
\item Latch the registers given in fields A and B into the ALU
\item Copy the result of the previous ALU operation into the register given by C
\item Rotate the register file forward (0->1, 1->2 .. 15->0) by D steps.
\item Perform the ALU operation F (whose result will be available for the next instruction)
\end{itemize}

The processor is to be part of a 4 core cluster and to run at approximately 1.2GHz.

\begin{enumerate}
\item Draw a block diagram for a reasonably efficient performance-orientated microarchitectural implementation of this architecture. Give the latency and IPC of your design. \fullmarks{6}
\item Why are branches a limited factor in modern CPU performance? Outline three techniques for improving the latency of branches \fullmarks{4}
\item Design a suitable cache, TLB and page table for this processor and comment on its performance characteristics, in particular on why you made the design choices you did. \fullmarks{4}
\item Write a SystemVerilog module to compute $x^y$, where $x$ and $y$ are both integer and unsigned, and the result will fit in 32 bits. \fullmarks{6}
\end{enumerate}
\end{question}
\end{document}


